Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/advup.tex

This exploration can be extended to schemes of the form
\begin{equation}
  \label{eq:explore}
	a^k_\deltat = \pi^\text{explore}_\deltat(s^k_\deltat, z^k_\deltat)
\end{equation}
with $(z^k_\deltat)_k$ a sequence of random variables, independant from the $a$'s and $s$'s.
A sufficient condition for the exploratory policy to admit a time continuous
limit is for
$z_\deltat$ to admit a limit, i.e. that the sequence $z_\deltat$ converges to a
well defined continuous stochastic process $z$ as $\deltat$ goes to $0$.
% For instance, $\varepsilon$-greedy exploration naturally falls in this framework, \TODO{[[CT would like to give these details, LB thinks it is not necessary:]] with each $z^k_\deltat$
% being a pair composed of a bernoulli random variables $b^k_\deltat$ with probability of being $1$ equal to $\varepsilon$,
% and of a uniform categorical random variable $\xi^k_\deltat$ on actions. Exploratory actions are then selected as
% \begin{equation}
% 	a^k_\deltat = (1 - b^k_\deltat) \text{argmax}_{a'} Q^\pi_\deltat(s, a') + b^k_\deltat \xi^k_\deltat.
% \end{equation}}

% \TODO{I'm convinced that this is true, reviewers might not be.}

On the other hand, the same argument cannot be applied to $\varepsilon$-greedy
exploration, as the $z_\deltat$'s used to define it do not converge to a 
well defined stochastic process, but to a white noise.\footnote{\TODO{$\varepsilon$-greedy
		does not, in general, converges to a well defined exploration scheme in continuous time.
		For instance, if actions directly affects position, $\varepsilon$-greedy results in white-noise
trajectories in state space. Show this in more detail in appendix ?}}

To obtain a temporally coherent exploration scheme in discrete action environment
$z_\deltat$ is chosen to be a discretization of a $|\mathcal{A}|$ dimensional
continuous OU process, and set
\begin{equation}
  \pi^\text{explore}(s_t, z_t)= \text{argmax}_{a'} \left(Q(s, a') + z_t[a']\right)
\end{equation}
where $z_t[a']$ denotes the $a'$-th component of the discretized OU process at time
$k$. The resulting exploration scheme converges to a proper time continuous exploration scheme.

>>>>

This exploration can be extended to schemes of the form
\begin{equation}
  \label{eq:explore}
	a^k_\deltat = \pi^\text{explore}_\deltat(s^k_\deltat, z^k_\deltat)
\end{equation}
with $(z^k_\deltat)_k$ a sequence of random variables, independant from the $a$'s and $s$'s.
A sufficient condition for the exploratory policy to admit a time continuous
limit is for
$z_\deltat$ to admit a limit, i.e. that the sequence $z_\deltat$ converges to a
well defined continuous stochastic process $z$ as $\deltat$ goes to $0$.
% For instance, $\varepsilon$-greedy exploration naturally falls in this framework, \TODO{[[CT would like to give these details, LB thinks it is not necessary:]] with each $z^k_\deltat$
% being a pair composed of a bernoulli random variables $b^k_\deltat$ with probability of being $1$ equal to $\varepsilon$,
% and of a uniform categorical random variable $\xi^k_\deltat$ on actions. Exploratory actions are then selected as
% \begin{equation}
% 	a^k_\deltat = (1 - b^k_\deltat) \text{argmax}_{a'} Q^\pi_\deltat(s, a') + b^k_\deltat \xi^k_\deltat.
% \end{equation}}
To obtain a temporally coherent exploration scheme in discrete action environment
$z_\deltat$ is chosen to be a discretization of a $|\mathcal{A}|$ dimensional
continuous OU process, and set
\begin{equation}
  \pi^\text{explore}(s_t, z_t)= \text{argmax}_{a'} \left(Q(s, a') + z_t[a']\right)
\end{equation}
where $z_t[a']$ denotes the $a'$-th component of the discretized OU process at time
$k$. The resulting exploration scheme converges to a proper time continuous exploration scheme,
and is non trivial for most $Q$'s.

Contrary to this discrete action exploration scheme, $\varepsilon$-greedy
exploration is likely to not explore, i.e. to collapse to a deterministic
policy when $\deltat$ goes to $0$. Indeed, one can prove that in a near
continuous deterministic environment, the exploration policy resulting from
applying $\varepsilon$ greedy exploration to a constant exploitation policy
converges to a determinist policy as $\deltat$ goes to $0$. More precisely, let
$(a_\deltat)$ a sequence of i.i.d. actions of distribution $p_A$, (for instance
the sequence of actions generated by $\varepsilon$-greedy exploration on a
constant policy). Then, as $\deltat$ goes to $0$, trajectories generated by
interacting with the environment using the $a$'s converge to solutions of
\begin{equation}
	ds_t = \E_{a\sim p_A}\left[F(s_t, a)\right]dt
\end{equation}
where the expectation cancels the exploration noise.
